%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}
\usepackage{xspace}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{color, colortbl}
\usepackage[all]{nowidow}
\usepackage[inline]{enumitem}
\usepackage[scaled]{beramono}
\usepackage{booktabs} % For formal tables
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{multirow}
\usepackage{balance}
\usepackage{listings}
%\usepackage{microtype}
\usepackage{tcolorbox}
\usepackage{cleveref}
\usepackage{soul}
\usepackage{lscape}
\usepackage{lineno}
%\usepackage[disable]{todonotes}
%%
%% \BibTeX command to typeset BibTeX logo in the docs


\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

\begin{document}

\title{The Name of the Title is Hope}

\title{\CT: Using collaborative filtering to recommend Github topics}

%\author{Juri Di Rocco}
%\affiliation{%
% \institution{Universit\'a degli studi dell'Aquila}
%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%  \city{Hekla}
%  \country{Iceland}}
%}
%\email{juri.dirocco@univaq.it}



%\renewcommand{\shortauthors}{Juri Di Rocco, et al.}
\input{commands}
\definecolor{Gray}{gray}{0.9}



\begin{abstract}
Collaborative filtering is a well-founded technique widely used in the recommendation system domain. During recent years, a plethora of approaches have been developed to provide the users with relevant items. Considering the open-source software (OSS) domain, \GH has gained the head role in storing, analyzing and maintaining a huge number of repositories. To represent the stored projects in an effective manner, in 2017 \GH introduced the possibility to classify them employing topics. However, such labeling activity should be carefully conducted to avoid negative effects on project popularity.
In this paper, we present \CT, a recommender system to assist open source software developers in selecting suitable topics for the repositories. \CT exploits a collaborative filtering technique to recommend libraries to developers by relying on the set of initial topics, which are currently included in the project being. To assess the quality of the approach, we exploit a recent work in this domain and validate both of them using different metrics. The results show that \CT outperforms it in all the examined aspects. More interesting, combining the two approaches improves the overall prediction performances.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, collaborative filtering, topic recommender}

\maketitle
	\section{Introduction}
\label{sec:Introduction}
\input{src/Introduction}




\section{Related Work}
\label{sec:RelatedWorks}
\input{src/RelatedWork}



\section{Proposed approach}
\label{sec:ProposedApproach}
\input{src/ProposedApproach}

\section{Evaluation}		
\label{sec:Evaluation}
\input{src/Evaluation}

\section{Results}
\label{sec:ExperimentalResults}
\input{src/ExperimentalResults}


\section{Threats to validity}
\label{sec:Threats}
\input{src/Threats}

\section{Conclusions and Future Work}
\label{sec:Conclusions}
\input{src/Conclusions}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{ESEM2020}

%%
%% If your work has an appendix, this is the place to put it.
\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
