\GH is nowadays among the most popular platforms to handle and maintain OSS projects. 
Topics have been introduced in 2017 to promote projects' visibility on the 
platform. 
%Although a couple of works face the problem, there are additional challenges 
%to be faced. 
In this work, we presented \TF, a collaborative filtering-based recommender 
system to suggest \GH topics.  By encoding repositories and related topics in a 
graph-based representation, we built a project-topic matrix and applied a 
syntactic-based similarity function to predict missing topics.
%To assess the prediction performances, we compared \TF with a well-founded work based on an 
%ML technique in terms of success rate and accuracy. The results show that \TF 
%outperforms the opponent with a relevant improvement of the mentioned metrics. 
To assess the prediction performances, we combined our approach with a well-founded system based on an ML algorithm, \ie \MNB. In particular, by taking as input in \TF, the 
output produced by \MNB, we showed that by means of a combined usage of such 
approaches, it is possible to obtain a significant boost in topic predictions. 
Nevertheless, the accuracy did not reach higher values in all the experimental 
settings. To our best knowledge, this depends very much on the similarity function used in 
the recommendation engine as well as on the heterogeneity of the dataset. Thus, 
we plan to extend \TF by adding different degrees of similarity, \eg 
semantic analysis on topics. Moreover, we can enlarge the evaluation by 
considering other common metrics in the collaborative filtering domain such as 
sales diversity and novelty. All of this is planned as future work.
