\GH is nowadays the most popular platform to handle and maintain OSS projects. Topics have been introduced in 2017 to promote the project's visibility on the platform. Although a couple of works face the problem, there are additional challenges to be faced. 
In this work, we have presented \CT, a collaborative filtering based recommender system to suggest \GH topics.  By representing repositories and related topics in a graph format, we built a user-item matrix and apply a syntactic-based similarity function to predict missing topics. To assess the prediction performances, we compared \CT with a well-founded work based on an ML technique in terms of success rate and accuracy. The results show that \CT outperforms the opponent with a relevant improvement of the mentioned metrics. Furthermore, we combined the two approaches in an \emph{entangled} evaluation to explore possible enhancements. We figured out that \CT gained a significant boost in prediction performances by employing the \MNB outcomes as input topics. Nevertheless, the accuracy didn't reach higher values in all the experimental settings. To our best knowledge, it depends on the similarity function used in the recommendation engine as well as on the heterogeneity of the dataset. Thus, we are planning to extend \CT by adding different degrees of similarity \ie semantic analysis on topics, README encoding to name a few. Moreover, we can enlarge the evaluation by considering other common metrics in the collaborative filtering domain such as sales diversity and novelty. These augmentations will be considered as possible future work.
