In recent years, the software developer community has intensively exploited open source 
repositories during their daily activities. \GH has become one of the most
popular platforms that aggregate these projects and support collaborative 
development activities~\cite{7832894}. \GH recently introduced the possibility 
to tag repositories employing 
\emph{topics}\footnote{\url{https://help.github.com/en/github/administering-a-repository/classifying-your-repository-with-topics}}
 intending to foster the popularity and promote information discovery about 
available projects.\footnote{Hereafter the terms \GH  \emph{``projects''} and \emph{``repositories''} 
are used 
interchangeably.} Topics are terms used to characterize repositories and to 
facilitate their discoverability from software developers who are searching 
for existing projects providing them with some reusable features. 

Assigning repositories with wrong topics can compromise their popularity and 
reachability. To deal with such problems, in 2017 \GH introduced a 
mechanism named Repo-Topix to suggest topics by relying on various information 
retrieval techniques \cite{repo-topix}. To improve Repo-Topix 
and to explore additional recommendation strategies, a recent work (named \MNB 
hereafter) proposes a Multinomial Na\"ive Bayesian network to 
recommend relevant topics starting from the README file(s) of the repository of 
interest \cite{10.1145/3383219.3383227}. However, such a tool can recommend 
only \emph{featured} topics, \ie a set of topics, which are curated by 
\GH.\footnote{\url{https://github.com/topics}}


In this paper, we propose \TF, a recommender system that extends the 
recommendation capabilities of the \MNB approach previously mentioned to 
non-featured topics by exploiting a collaborative filtering technique, a widely used 
algorithm in the recommender system domain 
\cite{Schafer:2007:CFR:1768197.1768208}. Given an initial set of topics already 
assigned to the \GH repository of interest, we encode it in a graph-based 
structure to represent the mutual relationships between repositories and 
topics. From this, a repository-topic matrix is created by following the 
typical user-item structure used in existing collaborative filtering 
applications. Then, we compute a similarity function based on featured vectors 
to recommend the most similar topics.

We evaluate the \TF's prediction performances by changing different parameters 
as well as comparing it with \MNB. As a direct comparison between the two approaches %, \ie \MNB and \TF 
is not
possible due to their internal construction, 
we used a well-defined set of metrics used in the literature to evaluate them by 
considering different datasets. More importantly, we showed that by augmenting \MNB with \TF, we are able to provide more relevant topics, given a repository. In this sense, we substantially improve the performance of the original \MNB approach.

%Furthermore, we also investigated the combined 
%adoption of \MNB and \TF to investigate the potential benefits of their 
%combined 
%use. 

The contributions of this paper are as follows:
\begin{itemize}
	\item By considering \GH topics as a product to recommend, we improve 
	repositories' popularity by suggesting a list of relevant topics;
	\item We assess the quality of the work employing a well-defined set of 
	metrics commonly used in the recommendation system domain, \ie success rate, 
	accuracy, and catalog coverage;
	\item Considering a well-founded approach, we improve it by recommending an 
	extended set of topics.  
\end{itemize}

The paper is structured into the following sections. Section \ref{sec:Background} presents the 
context of this work by means of a motivating example. In Section 
\ref{sec:ProposedApproach}, we introduce the \TF approach, with its evaluation being 
presented in Section \ref{sec:Evaluation}. Section 
\ref{sec:ExperimentalResults} discusses relevant findings, and the related work is 
summarized in  Section \ref{sec:RelatedWorks}. Finally, we conclude the paper 
and discuss future work in Section \ref{sec:Conclusions}.
